Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-14 report/report.tex
Fix typos in abstract

\begin{abstract}
Modeling a city in 3D has long been a topic of interest in field of computer graphics.
It is often desirable to recreate real-world cities in 3D applications such as urban design software and video games, and the topic of 3D city reproduction comes with its own set of unique challenges.
So far there have been a lot of research in modelling of 3D road networks, but these projects have often focused on the road networks designated for cars and public transit, and seldom on pedestrian footpaths.
This project assesses the feasibility of reconstructing a city from OpenStreetMap (OSM) road and building data, and will focus on the feasibility of including of pedestrian footpaths, by focusing on OSM road and building data in the Stockholm metropolitan area.

>>>>

\begin{abstract}
Modeling cities in 3D has long been a topic of interest in field of computer graphics.
It is often desirable to recreate real-world cities in 3D applications such as urban design software and video games, and the topic of 3D city reproduction comes with its own set of unique challenges.
So far there have been a lot of research in modelling of 3D road networks, but these projects have often focused on the road networks designated for cars and public transit, and seldom on pedestrian footpaths.
This project assesses the feasibility of reconstructing a city from OpenStreetMap (OSM) road and building data, and will focus on the feasibility of including pedestrian footpaths, by focusing on OSM road and building data in the Stockholm metropolitan area.
